Useful R tidbits: Social Networks

### 2022-02-08 _academics/ps753-glossary/ps753-glossary.Rmd
build
Add useful bits link

degree
: the number of links that a node has; the number of nodes it's connected to

@@

centralization
: a property of a graph, referring to its overall cohesion; comparing most central point to all other points; ratio of the actual sum of differences to the maximum possible sum of differences

>>>>

(vertex) degree
: the number of links that a node has; the number of nodes it's connected to

@@

(closeness) centrality
: (forthcoming)

(betweenness) centrality
: (forthcoming)

(eigenvector) centrality
: (forthcoming)

centralization
: a property of a graph or network, referring to its overall cohesion; comparing most central point to all other points; ratio of the actual sum of differences to the maximum possible sum of differences

### 2022-02-08 _academics/ps753-useful-r-tidbits/ps753-useful-r-tidbits.Rmd
Add useful bits link

---
title: "Useful R tidbits: Social Neteorks"
description: |
  Tasty R snacks that do useful things in Social Networks
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-08
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

@@

This document contains R snippets pertaining to work in the [Social Networks class](../ps753/index.html). There is also one for the [Machine Learning class](../ms797/index.html).

>>>>

---
title: "Useful R tidbits: Social Networks"
description: |
  Tasty R snacks that do useful things in Social Networks
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-08
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

@@

This document contains R snippets pertaining to work in the [Social Networks class](../ps753/index.html). There is also one for the [Machine Learning class](../ms797-useful-r-tidbits/index.html).
